\bf Adaption of the Chumbley Score to matching of bullet striation marks

### 2018-05-22 doc/paper.tex
some more proofing

% !TeX program = pdfLaTeX
\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{graphicx,psfrag,epsf}
\usepackage{enumerate}
\usepackage{natbib}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{subfig}
\usepackage[table]{xcolor}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{hyperref}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}

@@

\caption{Percent of failed land-to-land comparisons using an optimization window $w_o = 120$ and a coarseness of $c = 0.25$. With an increase in the size of the validation window  a higher percentage of tests fails under both methods (CS1) and (CS2), but the percentage of failed tests is much smaller under (CS2). Observed failure rates are higher than expected rates.}\label{fig:fails}
\end{figure}

@@

\autoref{fig:profile-sketch} gives an overview of the effect of
different coarseness parameters: from left to right, coarseness levels
\(c\) are varied in steps of 0.05 from 0.1 to 0.3. The top row shows
resulting signatures after smoothing the profile shown in
Figure\textasciitilde{}\ref{fig:sigs-profiles} with different levels of
coarseness. The histograms in the bottom row show the relative optimal
location \(t^*\). Optimal locations are distributed uniformly once
(sub-)class characteristics are removed. However, for coarseness values
of \(c > 0.20\) we see quite distinct boundary effects: optimal
locations \(t^*\) are found at the very extreme ends of a profile more
often than one would expect based on a uniform distribution.

{\textcolor{blue}{The key effect of the optimal locations and thereby the coarseness is seen in the number of failed tests. Irrespective of whether CS1 or CS2 is being used, if the relative optimal locations are at the boundaries we will see an increase in the number of failed tests. A balance is therefore needed in the selection of the coarseness parameter which reduces the boundary effect but also does not remove important individual characteristics}}

@@

\hypertarget{type-ii-error-rates}{%
\subsection{Type II error rates}\label{type-ii-error-rates}}

\autoref{fig:type2} gives an overview of the type 2 error of methods CS1
and CS2 across a range of different optimization windows \(w_o\).

{\centering \includegraphics[width=0.9\textwidth]{figures/type2-1}

\caption{Type II error rates observed across a range of window sizes for optimization $w_o$. For a window size of $w_o = 130$ we see a minimum in type II error rate across all type I rates considered. Smaller validation sizes $w_v$ are typically associated with a smaller type II error.}\label{fig:type2}
\end{figure}

\autoref{fig:roc} gives an overview of ROC (Receiver operating
characteristic) curves for methods CS1 and CS2 over a range of different
optimization window sizes \(w_o\). The different color hues represent
the two methods CS1 (red) and CS2 (blue). The ROC curves show the
superior performance of CS2 over CS1. Generally, an optimization window
\(w_o\) of 150 pixels or more leads to the best performance with respect
to ROC curves.

@@

>>>>

% !TeX program = pdfLaTeX
\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{graphicx,psfrag,epsf}
\usepackage{enumerate}
\usepackage{natbib}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{adjustbox}
\usepackage{multirow}
\usepackage{subfig}
\usepackage[table]{xcolor}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{hyperref}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}

@@

\caption{Percent of failed land-to-land comparisons using an optimization window $w_o = 120$ and a coarseness of $c = 0.25$. With an increase in the size of the validation window  a higher percentage of tests fails under both methods (CS1) and (CS2), but the percentage of failed tests is much smaller under (CS2). Observed failure rates of (CS1) are higher than expected rates.}\label{fig:fails}
\end{figure}

@@

\autoref{fig:profile-sketch} gives an overview of the effect of
different coarseness parameters: from left to right, coarseness levels
\(c\) are varied in steps of 0.05 from 0.1 to 0.3. The top row shows
resulting signatures after smoothing the profile shown in
\autoref{fig:sigs-profiles} with different levels of coarseness. The
histograms in the bottom row show the relative optimal location \(t^*\).
Optimal locations are distributed uniformly once (sub-)class
characteristics are removed. However, for coarseness values of
\(c > 0.20\) we see quite distinct boundary effects: optimal locations
\(t^*\) are found at the very extreme ends of a profile more often than
one would expect based on a uniform distribution.

The key effect of the optimal locations and thereby the coarseness is
seen in the number of failed tests. Irrespective of whether CS1 or CS2
is being used, if the relative optimal locations are at the boundaries
we will see an increase in the number of failed tests. A balance is
therefore needed in the selection of the coarseness parameter which
reduces the boundary effect but does not remove important individual
characteristics. Based on \autoref{fig:profile-sketch} a coarseness
value of \(c = 0.15\) seems to be best suited to strike this balance for
this example. For the remainder of the analysis, we will use this value
for \(c\).

@@

\hypertarget{error-rate-assessment}{%
\subsection{Error rate assessment}\label{error-rate-assessment}}

\autoref{fig:roc} gives an overview of ROC (Receiver operating
characteristic) curves for methods CS1 and CS2 over a range of different
optimization window sizes \(w_o\) and two sizes for the validation
window \(w_v\) (shape). The different color hues represent the two
methods CS1 (red) and CS2 (blue). The ROC curves show the superior
performance of CS2 over CS1. Generally, an optimization window \(w_o\)
of 150 pixels or more leads to the best performance with respect to ROC
curves. Results based on a validation window of size \(w_v = 30\) are
generally better than results for \(w_v = 50\).

\autoref{fig:eer}
\autoref{tab:aucs}

@@

\begin{table}[ht]
\centering
\begin{adjustbox}{max width=\textwidth}
\begin{tabular}{rrrlrrl}
  \hline
  & \multicolumn{3}{l}{\bf CS1} & \multicolumn{3}{l}{\bf CS2} \\
$w_o$ & \bf FPR & \bf FNR & \bf AUC (95\% C.I.) & \bf FPR & \bf FNR & \bf AUC (95\% C.I.) \\ 
  \hline
90 & 0.068 & 0.330 & 0.850 (0.835, 0.865) & 0.075 & 0.242 & 0.877 (0.863, 0.890) \\ 
  120 & 0.065 & 0.309 & 0.864 (0.850, 0.878) & 0.072 & 0.236 & 0.890 (0.877, 0.903) \\ 
  130 & 0.065 & 0.317 & 0.863 (0.850, 0.877) & 0.072 & 0.224 & 0.898 (0.886, 0.910) \\ 
  140 & 0.065 & 0.304 & 0.873 (0.859, 0.886) & 0.071 & 0.229 & 0.902 (0.891, 0.914) \\ 
  150 & 0.067 & 0.326 & 0.863 (0.850, 0.877) & 0.072 & 0.225 & 0.904 (0.892, 0.916) \\ 
  180 & 0.061 & 0.326 & 0.877 (0.864, 0.890) & 0.070 & 0.229 & 0.907 (0.896, 0.919) \\ 
  210 & 0.064 & 0.342 & 0.865 (0.851, 0.878) & 0.066 & 0.231 & 0.906 (0.895, 0.918) \\ 
   \hline
\end{tabular}
\end{adjustbox}
\caption{\label{tab:aucs} Overview of results as shown in Figures \ref{fig:roc} and \ref{fig:eer}. FPR is the observed rate of false positives (for a fixed level $\alpha = 0.05$) or type I error rate, FNR is the false negative rate or type II eror rate. Area under the curve (AUC) is shown with confidence intervals \citep{delong}. CS2 significantly outperforms CS1 with respect to its predictive power. }
\end{table}
